Arbeidskrav i MSB205

### 2022-11-06 MSB205NY.qmd
nesten ferdig

---
title: "Arbeidskrav i MSB205"
author: 
- Jonathan Christoffersen
- Daniel Karstad
format: html
editor: visual
lang: no-NB
---

@@

# Oppgave 1

@@

@@

## i. Funn fra EDA

@@

>>>>

---
title: "Arbeidskrav i MSB205"
author: 
- Jonathan Christoffersen
- Daniel Karstad
date: "Innleveringsfrist: 10.11.2022"
format: html
editor: visual
lang: no-NB
---

@@

# Oppgave 1 - Artikkelsammendrag

@@

Har sett over definisjonene.

@@

## i. Funn fra EDA*

@@

```{r}
SDEM_seed <- errorsarlm(mod3, data = kc_house_data_4444, listw = kc_house_data_4444_W,
                        Durbin = as.formula(~ bedrooms + bathrooms + sqft_living +
                                                sqft_living15 + sqft_lot + sqft_lot15 +
                                                sqft_above + floors + grade + yr_built +
                                                yr_renovated + waterfront + condition +
                                                view + dist_cbd_km + EHD_percen +
                                                low + high))
```

```{r}
SLX_seed <- lmSLX(mod3, data = kc_house_data_4444, listw = kc_house_data_4444_W,
                  Durbin =  as.formula(~ bedrooms + bathrooms + sqft_living +
                                           sqft_living15 + sqft_lot + sqft_lot15 +
                                           sqft_above + floors + grade + yr_built +
                                           yr_renovated + waterfront + condition + 
                                           view + dist_cbd_km + EHD_percen + 
                                           low + high))
```

```{r}
SEM_seed <- errorsarlm(mod3, data = kc_house_data_4444, listw = kc_house_data_4444_W, 
                       Durbin = FALSE)
```

```{r}
summary(impacts(SDEM_seed), zstats = TRUE)
```

```{r}
huxreg("SEM" = SEM_seed, "OLS" = hedon3_seed, 
    error_format = "[{statistic}]",
    note = "{stars}. T statistic in brackets.")
```

```{r}
LR.Sarlm(SDEM_seed, SEM_seed)
LR.Sarlm(SDEM_seed, SLX_seed)
```

```{r}
LR1.Sarlm(SDEM_seed)
```

```{r}
Hausman.test(SEM_seed)
```

```{r}
bptest.Sarlm(SEM_seed, studentize = TRUE)
```

```{r}
moran.plot(residuals(hedon3_seed), listw = kc_house_data_4444_W10)
```

```{r}
moran.plot(residuals(SDEM_seed), listw = kc_house_data_4444_W10)
```

```{r}
moran.test(residuals(SDEM_seed), listw = kc_house_data_4444_W10)
```

# Oppgave 9

```{r}
set.seed(420)
kc_houses_env_var_omit_2000 <- kc_houses_env_var_omit[sample(1:nrow(
    kc_houses_env_var_omit), 2000, replace = FALSE), ]
```

```{r}
hedon3_2000 <- lm(mod3, data = kc_houses_env_var_omit_2000)
```

```{r}
huxreg("Full" = hedon3, "2000 Seed" = hedon3_2000, "666 Seed" = hedon3_seed, 
    error_format = "[{statistic}]",
    note = "{stars}. T statistic in brackets.")
```

```{r}
kc_house_data_2000_mat_nb <- knearneigh(kc_houses_env_var_omit_2000, k = 3)
kc_house_data_2000_nb <- knn2nb(kc_house_data_2000_mat_nb)
kc_house_data_2000_W <- nb2listw(kc_house_data_2000_nb, style = "W")
kc_house_data_2000_mat_nb10 <- knearneigh(kc_houses_env_var_omit_2000, k = 10)
kc_house_data_2000_nb10 <- knn2nb(kc_house_data_2000_mat_nb10)
kc_house_data_2000_W10 <- nb2listw(kc_house_data_2000_nb10, style = "W")
```

```{r}
lm.morantest(hedon3_2000, kc_house_data_2000_W)
lm.morantest(hedon3_2000, kc_house_data_2000_W10)
```

```{r}
moran.plot(log(kc_houses_env_var_omit_2000$price), listw = kc_house_data_2000_W, labels = FALSE, pch = 20, cex = 0.3)
```

```{r}
moran.plot(log(kc_houses_env_var_omit_2000$price), listw = kc_house_data_2000_W10, labels = FALSE, pch = 20, cex = 0.3)
```

```{r}
kc_lagrange_3_2000 <- lm.LMtests(hedon3_2000, kc_house_data_2000_W, 
               test = "all")
kc_lagrange_3_2000
```

```{r}
kc_lagrange_10_2000 <- lm.LMtests(hedon3_2000, kc_house_data_2000_W10, 
               test = "all")
kc_lagrange_10_2000
```

```{r}
SDEM_2000 <- errorsarlm(mod3, data = kc_houses_env_var_omit_2000, listw = kc_house_data_2000_W, 
                        Durbin = as.formula(~ bedrooms + bathrooms + sqft_living + sqft_living15 +
                                                sqft_lot + sqft_lot15 + 
                                                sqft_above + floors + grade + yr_built + 
                                                yr_renovated + waterfront + condition + 
                                                view + dist_cbd_km + EHD_percen + 
                                                low + high))
```

```{r}
SLX_2000 <- lmSLX(mod3, data = kc_houses_env_var_omit_2000, listw = kc_house_data_2000_W, 
                  Durbin =  as.formula(~ bedrooms + bathrooms + sqft_living + sqft_living15 +
                                           sqft_lot + sqft_lot15 + sqft_above + floors + grade +
                                           yr_built + yr_renovated + waterfront + condition +
                                           view + dist_cbd_km + EHD_percen + low + high))
```

```{r, cache=TRUE}
SEM_2000 <- errorsarlm(mod3, data = kc_houses_env_var_omit_2000, listw = kc_house_data_2000_W, 
                       Durbin = FALSE)
```

```{r}
summary(impacts(SDEM_2000), zstats = TRUE)
```

```{r}
huxreg("SEM" = SEM_2000, "OLS" = hedon3_2000, 
    error_format = "[{statistic}]",
    note = "{stars}. T statistic in brackets.")
```

```{r}
LR.Sarlm(SDEM_2000, SEM_2000)
LR.Sarlm(SDEM_2000, SLX_2000)
```

```{r}
LR1.Sarlm(SDEM_2000)
```

```{r}
Hausman.test(SEM_2000)
```

```{r}
bptest.Sarlm(SEM_2000, studentize = TRUE)
```

```{r}
moran.plot(residuals(hedon3_2000), listw = kc_house_data_2000_W10)
```

```{r}
moran.plot(residuals(SDEM_2000), listw = kc_house_data_2000_W10)
```

```{r}
moran.test(residuals(SDEM_2000), listw = kc_house_data_2000_W10)
```

# Oppgave 10 - Konklusjon
